\question

\begin{proof}
    First, I argue by explicit construction that a polynomial as required
    exists, followed by a proof for the uniqueness of this construction.
    
    Construct, for each pair \((\alpha_i, \beta_i)\), a polynomial \(f_i(x)\)
    such that \(f_i(\alpha_j) = \delta_{ij}\cdot \beta_i \forall \) index pairs
    \((i, j)\). A choice for such a polynomial is:
    
    \begin{equation}
        f_i(x) = \beta_i\cdot\displaystyle\frac{
            \prod_{j\not = i} (x-\alpha_j)
        }{
            \prod_{j\not = i} (\alpha_i-\alpha_j)
        }
    \end{equation}

    which is a polynomial of degree \((n-1)\) satisfying the required criteria.
    The sum of all such polynomials produces the required result:

    \begin{equation}
        f(x) = \sum_{i=1}^{n} f_i(x)~.
    \end{equation}

    The existence of the required polynomial is proven. Assume now there are two
    distinct polynomials \(f(x)\) and \(g(x)\), each with degree less than
    \((n-1)\), satisfying the requirements. Thus, they each have monomial
    expansions of the form

    \begin{gather}
        f(x) = \sum_{j=0}^{n-1} a_j x^j \textnormal{ , and}\\
        g(x) = \sum_{j=0}^{n-1} b_j x^j ~.
    \end{gather}

    For each of these, plugging in the values of the given points, we get the
    linear systems

    \begin{align*}
        \sum_{j=0}^{n-1} a_j \alpha_1^j &= \beta_1 \\
        \sum_{j=0}^{n-1} a_j \alpha_2^j &= \beta_2 \\
                                        &\;\;\vdots \notag \\
        \sum_{j=0}^{n-1} a_j \alpha_n^j &= \beta_n
    \end{align*}

    and likewise for \(g(x)\), with the \(b_j\) as coefficients. This can be
    seen as a linear system given by the Vandermonde matrix and the vector
    \((\beta_j)\), with the vectors \((a_j)\) and \((b_j)\) as solutions to the
    system. However, from the previous question we know that the Vandermonde
    matrix is in fact of full rank, so there is a unique solution to this linear
    system, and thus the solution vectors must be equal, i.e., \(a_j = b_j
    \forall j \in \{1, 2, ..., n\}\). Consequently, \(f(x) = g(x)\), so we have
    a contradiction. There is thus a unique polynomial satisfying the given
    requirements.
\end{proof}