\begin{frame}
    \frametitle{Problem 3.6}

    \textbf{Problem. } Suppose \(E\) is a vector bundle over \(M\), and \(U\) is
    an open set containing \(p \in M\). Let \(s\) be a smooth section of
    \(E_U\). Show that there exists a smooth section \(t\) of \(E\) whose
    restriction to \(U\) agrees with \(s\) in a neighbourhood of \(p\).

\end{frame}

% define vector bundle and sections?

\begin{frame}
    
    Given a smooth section \(s\) of \(E_U\), construct a smooth function \(f\)
    over \(M\) such that it is uniformly \(1\) in a neighbourhood of \(p\) and
    \(0\) everywhere outside \(U\). 

    Note that \(f\cdot s\) is a smooth section of \(E_U\) as well. As it
    vanishes along the boundary, we can trivially extend it to a global smooth
    section

    \begin{gather}
        t(x) = \begin{cases}
            f(x)\cdot s(x) \text{ if } x \in U \\
            0 \text{ otherwise.}
        \end{cases}
    \end{gather}

\end{frame}

\begin{frame}
    
    By construction, it agrees with \(s\) in a neighbourhood of \(p\) when
    restricted. \(t\) is the required section.

    This only matches on a neighbourhood, can we do better? Can we define a
    section on a slice of the space and extend it globally?

\end{frame}

\begin{frame}
    \frametitle{Global Sections (lack thereof)}

    Consider a trivial bundle on \(\reals\) given by \(\reals \times \reals\).
    Construct a section on \(\reals \setminus \{0\}\) given by \(s(p) = (p,
    \frac{1}{p})\).\\

    Can we extend this to a section on the whole space? \\

    Note that we can still construct a global section that agrees with this
    section in a neighbourhood of any interior point of \(\reals \setminus
    \{0\}\).

\end{frame}